---
title: "Iterations and listcols"
author: "Jasmine Niu (jn2855)"
date: "2022-11-01"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
```

Let's look at a list.

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))

l
```

Accessing list items

```{r}
l$vec_numeric

l[[3]]

l[["mat"]]
```


normal distribution...

```{r}
list_norm =
  list(
    a = rnorm(20, 5, 4),
    b = rnorm(20, -12, 3),
    c = rnorm(20, 17, 4),
    d = rnorm(20, 100, 1)
  )

is.list(list_norm)
```


```{r}
mean_and_sd = function(x) {
  
  
  if(!is.numeric(x)) {
    stop("Z scores only work for numbers")

  }
  
  if(length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }  
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

Let's try to make this work.

```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```

Let's a `for` loop instead.

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])

}

output
```


## can we map??

we can map!!

```{r}
map(list_norm, mean_and_sd)

#first argument: can be a list, vector or data frame

output = map(.x = list_norm, ~ mean_and_sd(.x))
```

so...what about other functions?

```{r}
map(list_norm, var)
map(list_norm, summary)
```


map variants...

```{r}
map_dbl(list_norm, median)

map_df(list_norm, mean_and_sd)

map_dbl(list_norm, median, .id = "input")

#.id argument keeps the names of the elements in the input list

# output = map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y))
```


## list columns...

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    norm = list_norm
  )

listcol_df[["norm"]]

output = map(listcol_df[["norm"]], mean_and_sd)
```


can we add list columns and then what...

```{r}
listcol_df %>% 
  mutate(
    m_sd = map(norm, mean_and_sd) #map_df()
  ) %>% 
  select(-norm)
```

## What about something more realistic...

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

let's nest within weather stations...

```{r}
weather_nest_df = 
  weather_df %>% 
  nest(data = date:tmin)
```


Really is a list column!

```{r}
weather_nest_df[["data"]]

weather_nest_df %>% pull(data)
```


```{r}
weather_nest_df[["data"]][[1]]

lm(tmax ~ tmin, data = weather_nest_df[["data"]][[1]]) #y~x
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[2]]) 
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[3]]) 
```

Let's write a short lil ol function

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest_df[["data"]][[1]])

map(weather_nest_df[["data"]], weather_lm)
```


Can i do all this in a tidy way

```{r}
weather_nest_df %>% 
  mutate(
    model = map(data, weather_lm)
  )
```


unnesting

```{r}
weather_nest_df %>% 
  unnest(data)
```


## Napoleon!!


```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

What we did last time

```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```


```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

map(vec_urls, read_page_reviews)

napoleon_reviews = 
  tibble(
    page = 1:5,
    page_url = str_c(url_base, page)
  ) %>% 
  mutate(
    reviews = map(page_url, read_page_reviews)
  )

napoleon_reviews %>% 
  select(-page_url) %>% 
  unnest(reviews)
```

